### 2025-02-18 src/paper/paper.tex
typos fixed

The data from SchizConnect was filtered based on MRI field strength and clinical diagnosis. We retrieved only T1-weighted images (MPRAGE sequence) acquired using 3T MRI scanners. This was done to ensure uniformity of the data obtained. Figure~\ref{fig:raw_mri_volume_slices} presents the example of raw data.
\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\textwidth]{./figs/sample_volume.png} %
    \caption{Three image slices representing the average of a 3D column in three views: dorsal, lateral, and superior respectively}\label{fig:raw_mri_volume_slices}
\end{figure}

>>>>

The data from SchizConnect was filtered based on MRI field strength and clinical diagnosis. We retrieved only T1-weighted images (MPRAGE sequence) acquired using 3T MRI scanners. This was done to ensure uniformity of the data obtained. Figure~\ref{fig:raw_mri_volume_slices} presents the example of raw data.
\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\textwidth]{./figs/sample_volume.png} %
    \caption{Three image slices representing the average of a 3D column in three views: dorsal, lateral, and superior respectively.}\label{fig:raw_mri_volume_slices}
\end{figure}
